How to compute the fusion product of MV cycles in type A

### 2021-02-21 draft.tex
typos in lattice sec

\subsection{Lattices}
\label{ss:lat}
We will use the lattice model, so it is useful to recall the following definition.  Let $ R \subset K$ be two rings (usually, but not always, $K$ will be a field).  Let $ m \in \mathbb N$ and consider $ K^m $ as a $K$-module.   By restriction $ K^m$ can be viewed as an $R$-module.  An $R$-lattice in $M$ is an $R$-submodule $ L \subset K^m$ such that $ L $ is a free rank $ m $ $R$-module and $ L \otimes_R K = K^m $.  Equivalently, $ L = \Sp_R(v_1, \dots, v_m)$ where $v_1, \dots, v_m$ are free generators of $K^m$.

@@

We will be particularly interested in $\CC[t]$-lattices in $ \CC(t)^m$.  Given such a lattice $ L $ and a point $ a \in \CC$, the specialization of $ L $ at $ a $ is defined as
$$
L(a) := L \otimes_{\CC[t]} \CC\xt[t-a] \subset \CC\xT[t-a]\,.
$$
We say that $ L $ is trivial at $ a $ if $ L(a) = \CC\xt[t-a]^m$. For example, the lattice $(t-s)^{-1}\CC[t] \subset \CC(t)$ is trivial at any $a\ne s$.

@@

    \item To each $ A \in \TT_\mu$, we will associate an $m$\times$m$ matrix of polynomials $ g(A) = \left( g(A)_{ij} \right) \in M_m(\CC[t]) $ as follows.
       \begin{equation}
            g(A)_{ij} = \begin{cases} t^{\mu_i} - \sum_{k=1}^{\mu_i} A^k_{ji} t^{k-1} \text{ if $ i = j$} \\
             - \sum_{k=1}^{\mu_i} A^k_{ji} t^{k-1} \text{ if $ i \ne j$ }
        \end{cases}
    \end{equation}
    where $A^k_{ji}$ is the $k$th entry from the left of the last row of the $\mu_j\times\mu_i$ block of $A$. 
\jcom{I moved the definition here since it will be useful for defining the upper triangular stuff.}

>>>>

\subsection{Lattices}
\label{ss:lat}
We will use the lattice model, so it is useful to recall the following definition.  Let $ R \subset K$ be two rings (usually, but not always, $K$ will be a field \acom{When is $K$ not a field?}).  Let $ m \in \mathbb N$ \acom{we have already fixed $m$?} and consider $ K^m $ as a $K$-module.   By restriction $ K^m$ can be viewed as an $R$-module.  An $R$-lattice in $M$ \acom{what is $M$? should be $K^m$?} is an $R$-submodule $ L \subset K^m$ such that $ L $ is a free rank $ m $ $R$-module and $ L \otimes_R K = K^m $.  Equivalently, $ L = \Sp_R(v_1, \dots, v_m)$ where $v_1, \dots, v_m$ are free generators of $K^m$.

@@

We will be particularly interested in $\CC[t]$-lattices in $ \CC(t)^m$.  Given such a lattice $ L $ and a point $ a \in \CC$, the specialization of $ L $ at $ a $ is defined as
$$
L(a) := L \otimes_{\CC[t]} \CC\xt[t-a] \subset \CC\xT[t-a]^m\,.
$$
We say that $ L $ is trivial at $ a $ if $ L(a) = \CC\xt[t-a]^m$. \acom{Do we want to employ the notation $\cO_a$ and $\cK_a$ here?}
For example, the lattice $(t-s)^{-1}\CC[t] \subset \CC(t)$ is trivial at any $a\ne s$.

@@

    \item To each $ A \in \TT_\mu$, we will associate an $m\times m$ matrix of polynomials $ g(A) = \left( g(A)_{ij} \right) \in M_m(\CC[t]) $ as follows.
       \begin{equation}
            g(A)_{ij} = \begin{cases} t^{\mu_i} - \sum_{k=1}^{\mu_i} A^k_{ji} t^{k-1} \text{ if $ i = j$} \\
             - \sum_{k=1}^{\mu_i} A^k_{ji} t^{k-1} \text{ if $ i \ne j$ }
        \end{cases}
    \end{equation}
    where $A^k_{ji}$ is the $k$th entry from the left of the last row of the $\mu_j\times\mu_i$ block of $A$. 
\jcom{I moved the definition here since it will be useful for defining the upper triangular stuff.}
